%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Ime}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Adresa
    ~
    \href{mailto:mejl}{mejl}
    \href{brojtelefona}{brojtelefona}
    %\href{http://facebook.com/adrien}{fb://adrien}
  \section{languages}
    Jezici
  \section{programming}
    {\color{red} $\varheartsuit$} progJezici
\end{aside}

\section{interests}

interesovanja

\section{education}

\begin{entrylist}
  \entry
    {2007–2008}
    {M.Sc. magna cum laude}
    {IXXI, École Normale Supérieure de Lyon}
    {Majoring in Computer Science\\
    Specialization in Complex Systems}
  \entry
    {2006–2007}
    {B.Sc. magna cum laude}
    {École Normale Supérieure de Lyon}
    {Majoring in Computer Science}
  \entry
    {2003–2006}
    {Classes Préparatoires aux Grandes Écoles}
    {Lycée Fénelon, Lycée Louis le Grand, Paris}
    {Preparation for national competitive entrance exams to leading French ``grandes écoles'', specializing in mathematics and physics.}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {02–07 2009}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Visualization of complex networks.}}
  \entry
    {06–08 2008}
    {ISCPIF/CNRS, Paris}
    {Research Internship.}
    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
  \entry
    {06–08 2007}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Kernels in real world networks.}}
\end{entrylist}

\section{projects}

\begin{entrylist}
  \entry
    {2012}
    {Who did I forget ?}
    {\href{ }{ }}
    {Guest list recommendation for Facebook events based on friends already attending the event.}
  \entry
    {2011}
    {Fellows}
    {\href{ }{ }}
    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
\end{entrylist}

%\section{publications}

%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors.
%
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
